{How do we copy and paste?\\The semantic drift of quotations in blogspace}

### 2015-01-29 brains-protocol.tex
Minor phrasing

The final set of variables we consider, as well as their cross-correlations, can be seen in Figure~\ref{fig:feature-corrs-filtered}.\footnote{Note that feature values stem from different datasets which do not always encode the same words.
Indeed, we have data on frequency for about 22.6k words, on age of acquisition for 30.1k words, on number of phonemes for 123.4k words, number of synonyms 111.2k, and clustering coefficient 5.7k words.
Quite often then, not all features are available for all words in our dataset; % are encoded in only a subset of the features we use (if any at all); 
however this is not problematic since the analysis is done on a per-feature basis, all words need not be encoded in all features.}

>>>>

The final set of variables we consider, as well as their cross-correlations, can be seen in Figure~\ref{fig:feature-corrs-filtered}.\footnote{Note that feature values stem from different datasets which do not always encode the same words.
Indeed, we have data on frequency for about 22.6k words, on age of acquisition for 30.1k words, on number of phonemes for 123.4k words, number of synonyms 111.2k, and clustering coefficient 5.7k words.
Quite often then, not all features are available for all words in our dataset; % are encoded in only a subset of the features we use (if any at all); 
however this is not problematic since the analysis is done on a per-feature basis, and not all words need be encoded in all features.}
